Considering vertical sound speed uncertainty in the Beaufort Lens for more realistic range estimation between acoustic modems

### 2020-11-12 modem-paper/main.tex
affiliations for MIT-WHOI

\title[JASA/Sample JASA Article]{Considering vertical sound speed uncertainty in the Beaufort Lens for more realistic range estimation between acoustic modems}
\author{EeShan Bhatt}
\author{Oscar Viquez}
\author{Bradli Howard}
\author{Henrik Schmidt}
\affiliation{Department of Mechanical Engineering,  Massachusetts Institute of Technology, Cambridge, MA 02139, USA}

>>>>

\title[JASA/Sample JASA Article]{Considering vertical sound speed uncertainty in the Beaufort Lens for more realistic range estimation between acoustic modems}
\author{EeShan C. Bhatt}
\email{eesh@mit.edu}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, Cambridge, MA}
\affiliation{Applied Ocean Physics \& Engineering, Woods Hole Oceanographic Institution, Woods Hole, MA}
\author{Oscar Viquez}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, Cambridge, MA}
\author{Bradli Howard}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, Cambridge, MA}
\affiliation{Applied Ocean Physics \& Engineering, Woods Hole Oceanographic Institution, Woods Hole, MA}
\author{Henrik Schmidt}
\affiliation{Department of Mechanical Engineering, Massachusetts Institute of Technology, Cambridge, MA}
